Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-01 PandaEvolution.tex
refining subsection titles.

Compared to pilots, backfill has the disadvantage of limiting the amount of work
nodes that can be requested. Pilots are normal jobs: they can request as many
worker nodes for as much time as a queue can offer. On the contrary, jobs sized
on the basis of backfill information availability \jhanote{should be resource
availability or backfill queue information?}\mtnote{AFAIH, there is no dedicated
queue to backfill} depend on the number of worker nodes that cannot be given to
any other job in the Titan's queue.
% \sergeynote{any other job currently in the Titan's queue?}\mtnote{Better?}.

>>>>

Compared to pilots, backfill has the disadvantage of limiting the amount of
work nodes that can be requested. Pilots are normal jobs: they can request as
many worker nodes for as much time as a queue can offer. On the contrary, jobs
sized on the basis of backfill information availability depend on the number
of worker nodes that cannot be given to any other job in the Titan's queue. %
\sergeynote{any other job currently in the Titan's queue?}\mtnote{Better?}.
